plots

### 2024-10-02 plots.qmd
updater plots

```{r}

# Load necessary libraries
if (!require(ggplot2)) install.packages("ggplot2")
if (!require(gridExtra)) install.packages("gridExtra")
if (!require(reshape2)) install.packages("reshape2")
if (!require(gtable)) install.packages("gtable")  # Required for gtable_filter
if (!require(grid)) install.packages("grid")

@@

# Reshape the data to long format for ggplot
data_long <- melt(data, id.vars = 'rho', variable.name = 'Estimator', value.name = 'MSE')

# Create the grouped bar plot
mse_plot_n30_p3 <-ggplot(data_long, aes(x = Estimator, y = MSE, fill = factor(rho))) +
  geom_bar(stat = "identity", position = "dodge") +  # Group bars by rho
  scale_fill_brewer(palette = "Set3") +  # Use a distinct color palette
  labs(title = "MSE (n = 30, p = 3)",
       x = "Estimator", y = "Mean Squared Error (MSE)", fill = expression(rho)) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),  
        axis.title = element_text(size = 10),
        plot.margin = unit(c(1.5, 1.5, 1.5, 1.5), "cm"))

@@

# Reshape the data to long format for ggplot
data_long <- melt(data, id.vars = 'rho', variable.name = 'Estimator', value.name = 'CoverageProbability')

# Create the line plot for coverage probability
coverage_prob_plot_n30_p3 <- ggplot(data_long, aes(x = rho, y = CoverageProbability, color = Estimator)) +
  geom_point(size = 3) +                            # Add points
  geom_line(aes(group = Estimator), linetype = "dashed", size = 0.8) +  # Add dashed lines
  labs(title = "Coverage Probability (n = 30, p = 3)",
       x = expression(rho), y = "Coverage Probability") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 8),  
        axis.title = element_text(size = 10),
        plot.margin = unit(c(1.5, 1.5, 1.5, 1.5), "cm"))

@@

# Reshape the data to long format for ggplot
data_long <- melt(data, id.vars = 'rho', variable.name = 'Estimator', value.name = 'CI_Width')

# Create the grouped bar plot
ci_width_plot_n30_p3 <- ggplot(data_long, aes(x = Estimator, y = CI_Width, fill = factor(rho))) +
  geom_bar(stat = "identity", position = "dodge") +  # Group bars by rho
  scale_fill_brewer(palette = "Set3") +  # Use a distinct color palette
  labs(title = "Confidence Interval Width (n = 30, p = 3)",
       x = "Estimator", y = "Confidence Interval Width", fill = expression(rho)) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),   axis.title = element_text(size = 10),
  plot.margin = unit(c(1.5, 1.5, 1.5, 1.5), "cm"))

@@

# Create the data frame based on Table 15 (MSE values)
data <- data.frame(
  rho = c(0.60, 0.80, 0.85, 0.90, 0.95, 0.99),
  OLS = c(0.047,0.089,0.119,0.181,0.377,2.079),
  k1 = c(0.049,0.107,0.158,0.268,0.518,1.005),
  k2 = c(0.049,0.097,0.132,0.203,0.393),
  k3 = c(0.059,0.173,0.264,0.413,0.658,0.944),
  k4 = c(0.055,0.115,0.158,0.24,0.419,1.075),
  k5 = c(0.53,0.604,0.632,0.661,0.722,0.983),
  k6 = c(0.049,0.096,0.131,0.202,0.404,1.761),
  k7 = c(0.047,0.091,0.122,0.186,0.352,0.825),
  k8 = c(0.047,0.087,0.116,0.176,0.364,1.985),
  k9 = c(0.049,0.096,0.131,0.203,0.393,1.397),
  k10 = c(0.047,0.089,0.119,0.181,0.377,2.079),
  k11 = c(0.047, 0.089,0.119,0.181,0.377,2.079),
  k12 = c(0.047,0.09,0.12,0.182,0.378,2.039),
  k13 = c(0.049,0.096,0.13,0.202,0.39,1.327),
  k14 = c(0.565, 0.582,0.591,0.609,0.647,0.831),
  k15 = c(0.06,0.103,0.13,0.192,0.37,1.763),
  k16 = c(0.047,0.09,0.12,0.182,0.378,2.052),
  k17 = c(0.05,0.092,0.121,0.184,0.366,1.698),
  k18 = c(0.048,0.092,0.123,0.185,0.351,0.827),
  k19 = c(0.048,0.092,0.123,0.185,0.351,0.827)
)

# Reshape the data to long format for ggplot
data_long <- melt(data, id.vars = 'rho', variable.name = 'Estimator', value.name = 'MSE')

# Create the grouped bar plot
mse_plot_n100_p3 <- ggplot(data_long, aes(x = Estimator, y = MSE, fill = factor(rho))) +
  geom_bar(stat = "identity", position = "dodge") +  # Group bars by rho
  scale_fill_brewer(palette = "Set3") +  # Use a distinct color palette
  labs(title = " MSE  (n = 100, p = 3)",
       x = "Estimator", y = "Mean Squared Error (MSE)", fill = expression(rho)) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title = element_text(size = 10),
        plot.margin = unit(c(1.5, 1.5, 1.5, 1.5), "cm"))

@@

# Reshape the data to long format for ggplot
data_long <- melt(data, id.vars = 'rho', variable.name = 'Estimator', value.name = 'CoverageProbability')

# Create the line plot
coverage_prob_plot_n100_p3 <-ggplot(data_long, aes(x = rho, y = CoverageProbability, color = Estimator)) +
  geom_point(size = 3) +                            # Add points
  geom_line(aes(group = Estimator), linetype = "dashed", size = 0.8) +  # Add dashed lines
  labs(title = "Coverage Probability (n = 100, p = 3)",
       x = expression(rho), y = "Coverage Probability") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),  
        axis.title = element_text(size = 10),
        plot.margin = unit(c(1.5, 1.5, 1.5, 1.5), "cm"))

# plot for CI width n = 100, p = 3 , s = 1

@@

# Reshape the data to long format for ggplot
data_long <- melt(data, id.vars = 'rho', variable.name = 'Estimator', value.name = 'CI_Width')

# Create the grouped bar plot
ci_width_plot_n100_p3 <- ggplot(data_long, aes(x = Estimator, y = CI_Width, fill = factor(rho))) +
  geom_bar(stat = "identity", position = "dodge") +  # Group bars by rho
  scale_fill_brewer(palette = "Set3") +  # Use a distinct color palette
  labs(title = "Confidence Interval Width (n = 100, p = 3)",
       x = "Estimator", y = "Confidence Interval Width", fill = expression(rho)) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),  
        axis.title = element_text(size = 10),
        plot.margin = unit(c(1.5, 1.5, 1.5, 1.5), "cm"))

@@

# Arrange the plots in a 3x2 grid and add the legend separately
grid.arrange(
  mse_plot_n30_p3, mse_plot_n100_p3,
  coverage_prob_plot_n30_p3, coverage_prob_plot_n100_p3,
  ci_width_plot_n30_p3, ci_width_plot_n100_p3,
  # Add the legend here as a separate element
  ncol = 2, nrow = 3,  # One extra row for the legend
  heights = c(1.3, 1.3, 1.3),
  widths = c(1.3, 1.3))# The last row height for the legend

# Close the device to save the plot
dev.off()

```

>>>>

```{r}
# Load necessary libraries
if (!require(ggplot2)) install.packages("ggplot2")
if (!require(gridExtra)) install.packages("gridExtra")
if (!require(reshape2)) install.packages("reshape2")
if (!require(gtable)) install.packages("gtable") # Required for gtable_filter
if (!require(grid)) install.packages("grid")

@@

# Reshape the data to long format for ggplot
data_long <- melt(data, id.vars = "rho", variable.name = "Estimator", value.name = "MSE")

# Create the grouped bar plot
mse_plot_n30_p3 <- ggplot(data_long, aes(x = Estimator, y = MSE, fill = factor(rho))) +
  geom_bar(stat = "identity", position = "dodge") + # Group bars by rho
  scale_fill_brewer(palette = "Set3") + # Use a distinct color palette
  labs(
    title = "MSE (n = 30, p = 3)",
    x = "Estimator", y = "Mean Squared Error (MSE)", fill = expression(rho)
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.title = element_text(size = 10),
    plot.margin = unit(c(1.5, 1.5, 1.5, 1.5), "cm")
  )

@@

# Reshape the data to long format for ggplot
data_long <- melt(data, id.vars = "rho", variable.name = "Estimator", value.name = "CoverageProbability")

# Create the line plot for coverage probability
coverage_prob_plot_n30_p3 <- ggplot(data_long, aes(x = rho, y = CoverageProbability, color = Estimator)) +
  geom_point(size = 3) + # Add points
  geom_line(aes(group = Estimator), linetype = "dashed", size = 0.8) + # Add dashed lines
  labs(
    title = "Coverage Probability (n = 30, p = 3)",
    x = expression(rho), y = "Coverage Probability"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 8),
    axis.title = element_text(size = 10),
    plot.margin = unit(c(1.5, 1.5, 1.5, 1.5), "cm")
  )

@@

# Reshape the data to long format for ggplot
data_long <- melt(data, id.vars = "rho", variable.name = "Estimator", value.name = "CI_Width")

# Create the grouped bar plot
ci_width_plot_n30_p3 <- ggplot(data_long, aes(x = Estimator, y = CI_Width, fill = factor(rho))) +
  geom_bar(stat = "identity", position = "dodge") + # Group bars by rho
  scale_fill_brewer(palette = "Set3") + # Use a distinct color palette
  labs(
    title = "Confidence Interval Width (n = 30, p = 3)",
    x = "Estimator", y = "Confidence Interval Width", fill = expression(rho)
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1), axis.title = element_text(size = 10),
    plot.margin = unit(c(1.5, 1.5, 1.5, 1.5), "cm")
  )

@@

data <- data.frame(
  rho = c(0.60, 0.80, 0.85, 0.90, 0.95, 0.99),
  OLS = c(0.047, 0.089, 0.119, 0.181, 0.377, 2.079),
  k1 = c(0.049, 0.107, 0.158, 0.268, 0.518, 1.005),
  k2 = c(0.049, 0.097, 0.132, 0.203, 0.393, 1.396),
  k3 = c(0.059, 0.173, 0.264, 0.413, 0.658, 0.944),
  k4 = c(0.055, 0.115, 0.158, 0.24, 0.419, 1.075),
  k5 = c(0.53, 0.604, 0.632, 0.661, 0.722, 0.983),
  k6 = c(0.049, 0.096, 0.131, 0.202, 0.404, 1.761),
  k7 = c(0.047, 0.091, 0.122, 0.186, 0.352, 0.825),
  k8 = c(0.047, 0.087, 0.116, 0.176, 0.364, 1.985),
  k9 = c(0.049, 0.096, 0.131, 0.203, 0.393, 1.397),
  k10 = c(0.047, 0.089, 0.119, 0.181, 0.377, 2.079),
  k11 = c(0.047, 0.089, 0.119, 0.181, 0.377, 2.079),
  k12 = c(0.047, 0.09, 0.12, 0.182, 0.378, 2.039),
  k13 = c(0.049, 0.096, 0.13, 0.202, 0.39, 1.327),
  k14 = c(0.565, 0.582, 0.591, 0.609, 0.647, 0.831),
  k15 = c(0.06, 0.103, 0.13, 0.192, 0.37, 1.763),
  k16 = c(0.047, 0.09, 0.12, 0.182, 0.378, 2.052),
  k17 = c(0.05, 0.092, 0.121, 0.184, 0.366, 1.698),
  k18 = c(0.048, 0.092, 0.123, 0.185, 0.351, 0.827),
  k19 = c(0.048, 0.092, 0.123, 0.185, 0.351, 0.827)
)

# Reshape the data to long format for ggplot
data_long <- melt(data, id.vars = "rho", variable.name = "Estimator", value.name = "MSE")

# Create the grouped bar plot
mse_plot_n100_p3 <- ggplot(data_long, aes(x = Estimator, y = MSE, fill = factor(rho))) +
  geom_bar(stat = "identity", position = "dodge") + # Group bars by rho
  scale_fill_brewer(palette = "Set3") + # Use a distinct color palette
  labs(
    title = " MSE  (n = 100, p = 3)",
    x = "Estimator", y = "Mean Squared Error (MSE)", fill = expression(rho)
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.title = element_text(size = 10),
    plot.margin = unit(c(1.5, 1.5, 1.5, 1.5), "cm")
  )

@@

# Reshape the data to long format for ggplot
data_long <- melt(data, id.vars = "rho", variable.name = "Estimator", value.name = "CoverageProbability")

# Create the line plot
coverage_prob_plot_n100_p3 <- ggplot(data_long, aes(x = rho, y = CoverageProbability, color = Estimator)) +
  geom_point(size = 3) + # Add points
  geom_line(aes(group = Estimator), linetype = "dashed", size = 0.8) + # Add dashed lines
  labs(
    title = "Coverage Probability (n = 100, p = 3)",
    x = expression(rho), y = "Coverage Probability"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.title = element_text(size = 10),
    plot.margin = unit(c(1.5, 1.5, 1.5, 1.5), "cm")
  )

coverage_prob_plot_n100_p3
# plot for CI width n = 100, p = 3 , s = 1

@@

# Reshape the data to long format for ggplot
data_long <- melt(data, id.vars = "rho", variable.name = "Estimator", value.name = "CI_Width")

# Create the grouped bar plot
ci_width_plot_n100_p3 <- ggplot(data_long, aes(x = Estimator, y = CI_Width, fill = factor(rho))) +
  geom_bar(stat = "identity", position = "dodge") + # Group bars by rho
  scale_fill_brewer(palette = "Set3") + # Use a distinct color palette
  labs(
    title = "Confidence Interval Width (n = 100, p = 3)",
    x = "Estimator", y = "Confidence Interval Width", fill = expression(rho)
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.title = element_text(size = 10),
    plot.margin = unit(c(1.5, 1.5, 1.5, 1.5), "cm")
  )

@@

# Arrange the plots in a 3x2 grid and add the legend separately

complete_plot <-
  grid.arrange(
    mse_plot_n30_p3, mse_plot_n100_p3,
    coverage_prob_plot_n30_p3, coverage_prob_plot_n100_p3,
    ci_width_plot_n30_p3, ci_width_plot_n100_p3,
    # Add the legend here as a separate element
    ncol = 2, nrow = 3, # One extra row for the legend
    heights = c(1.3, 1.3, 1.3),
    widths = c(1.3, 1.3)
  ) # The last row height for the legend

jpeg("mse_plot.jpeg", width = 1800, height = 600, res = 150)

mse_plot <-
  grid.arrange(
    mse_plot_n30_p3, mse_plot_n100_p3,
    ncol = 2, nrow = 1, # One extra row for the legend
    heights = c(1.3),
    widths = c(1.3, 1.3)
  ) # The last row height for the legend
dev.off()

jpeg("cp_plot.jpeg", width = 2000, height = 1000, res = 150)

cp_plot <-
  grid.arrange(
    coverage_prob_plot_n30_p3, coverage_prob_plot_n100_p3,
    ncol = 2, nrow = 1, # One extra row for the legend
    heights = c(1.3),
    widths = c(1.3, 1.3)
  ) # The last row height for the legend

dev.off()

jpeg("ciw_plot.jpeg", width = 1800, height = 600, res = 150)

ciw_plot <-
  grid.arrange(
    ci_width_plot_n30_p3, ci_width_plot_n100_p3,
    ncol = 2, nrow = 1, # One extra row for the legend
    heights = c(1.3),
    widths = c(1.3, 1.3)
  ) # The last row height for the legend

# Close the device to save the plot
dev.off()
```
